{\small} High Performance P$^{3}$M N-body code: CUBEP3M

### 2012-06-29 Extendedpp.tex
new figures for pp_extended force

 \begin{figure*}%[ht]
  \begin{center}
    \includegraphics[width=3.2in]{graphs/densityForce_ppext=2_rebin_new.eps}
    \includegraphics[width=3.2in]{graphs/densityForce_fracErr_ppext=2_rebin_new.eps}
     \includegraphics[width=3.2in]{graphs/densityForce_ppext=2_rebin_new_N10.eps}
    \includegraphics[width=3.2in]{graphs/densityForce_fracErr_ppext=2_rebin_new_N10.eps}
    \caption{({\it top left}:) Gravity force in the P$^3$M algorithm, compared with the exact $1/r^{2}$ law,
  in the same CITA128 realization as that shown in Fig. \ref{fig:den_force_fracErr}, 
  except that the exact pp force has been extended to two fine mesh layers around each particle
  in the force test code.
  Particles in the that range follow the exact curve, then we observe a much smaller scatter at 
  distance of the order of 2 fine grid, compared to Fig. \ref{fig:den_force_fracErr}. 
  The NGP interpolation scheme is again responsible for the scatter, but the effect is suppressed with increasing distances, and further suppressed by averaging over many time steps.
  %\caption{
  ({\it top right}:) Fractional error on the force in the P$^3$M algorithm, in the radial (top) and tangential (bottom) directions.
  This was also obtained over a single time step.
  ({\it bottom row}:) Same as top row, but averaged over ten time steps.
    \label{fig:den_force_fracErr_ppext6}}
\end{center}
\end{figure*}

>>>>

 \begin{figure*}%[ht]
  \begin{center}
    \includegraphics[width=3.2in]{graphs/densityForce_ppext=2_rebin_new.eps}
    \includegraphics[width=3.2in]{graphs/densityForce_fracErr_ppext=2_rebin_new.eps}
     \includegraphics[width=3.2in]{graphs/densityForce_ppext=2_rebin_N10_new.eps}
    \includegraphics[width=3.2in]{graphs/densityForce_fracErr_ppext=2_rebin_N10_new.eps}
    \caption{({\it top left}:) Gravity force in the P$^3$M algorithm, compared with the exact $1/r^{2}$ law,
  in the same CITA128 realization as that shown in Fig. \ref{fig:den_force_fracErr}, 
  except that the exact pp force has been extended to two fine mesh layers around each particle
  in the force test code.
  Particles in the that range follow the exact curve, then we observe a much smaller scatter at 
  distance of the order of 2 fine grid, compared to Fig. \ref{fig:den_force_fracErr}. 
  The NGP interpolation scheme is again responsible for the scatter, but the effect is suppressed with increasing distances, and further suppressed by averaging over many time steps.
  %\caption{
  ({\it top right}:) Fractional error on the force in the P$^3$M algorithm, in the radial (top) and tangential (bottom) directions.
  This was also obtained over a single time step.
  ({\it bottom row}:) Same as top row, but averaged over ten time steps.
    \label{fig:den_force_fracErr_ppext6}}
\end{center}
\end{figure*}
